---
title: "inteli"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{inteli}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(inteli)
```

## Description

Parameter estimation via likelihood interval (LI) compared to traditional method (CI). This is the expanded version for 'LBI'- and 'wnl'-package, formulated by Kyun-Seop Bae <k@acr.kr>.

## Details

Currently available for estimating a single-group variance and a two-group variance ratio. 

## Author(s)

Minkyu Kim <mkim@acr.kr>

## References

1. Wilks SS. The Large-sample Distribution of the Likelihood Ratio for Testing Composite Hypotheses. Ann Math Stat. 1938;9(1):60-62.

2. Ruppert D, Cressie N, Carroll RJ. A Transformation/Weighting Model for Estimating Michaelis-Menten Parameters. Cornell University Technical Report 796. 1988.

3. Pawitan Y. In All Likelihood: Statistical Modelling and Inference Using Likelihood. 2001.

4. Lee MH, Bae KS. Likelihood interval for nonlinear regression. Transl Clin Pharmacol. 2023.
  
## Examples

x <- rnorm(20, 0, 1)
y <- rnorm(40, 0, 1)

varE(x)
varEplot(x, FALSE)
varEplot(x, TRUE)

varR(x, y)
varRplot(x, y, FALSE)
varRplot(x, y, TRUE)
